Interval Probability for Fuzzy Quantum Theories

### 2016-08-03 prob.tex
prob.tex \subsection{Interval-valued probability measures} updates...

An interval-valued probability measure can satisfy extra conditions.
It is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
For example, a special case of convex interval-valued probability
measures consists the lower probability (belief) as the left-end and
the upper probability (plausibility) as the right-end~\cite{GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
They are defined by Dempster~\cite{Dempster1967} and Shafer~\cite{Shafer1976}
and play an important role in the theory of non-additive belief.\footnote{\yutsung{If we want to use convex, we need to explain the physical
meaning of convex interval-valued probability measures...?}}

@@

>>>>

An interval-valued probability measure can satisfy extra conditions.
It is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
For example, a special case of convex interval-valued probability
measures consists the Dempster-Shafer belief function as the left-end
and the Dempster-Shafer plausibility as the right-end, which plays
an important role in the theory of non-additive belief~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
meaning of convex interval-valued probability measures...?}}

@@

Then, a wide variety of interval-valued probability measures can be
associated with real-valued probability measures.

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
